\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Fix typesetting problem

Another problem is caused by the move semantics for $\tload{}$ in the presence of multiple hardware threads.
In this setting, zeroing out the source memory location must happen atomically to avoid race conditions where two hardware threads end up reading the same linear capability to their registers.
This means that a $\tload{}$ of a linear capability will need to behave like an atomic operation, similar to a compare-and-swap instruction.
This is in principle not a problem except that a compare-and-swap is significantly slower than a regular $\tload{}$ (on the order of 10x slower or more).
When using \stktokens{}, loads of linear capabilities normally happen only when a thread has stored its return data capability on the stack and loads it back from there after a return.
Because the stack is a region of memory with very high thread affinity (no other hardware thread should access it, in principle), and which is accessed quite often, we are hopeful that well-engineered caching could reduce the high overhead of atomic loads of linear capabilities.
If such memory could be (usually) kept exclusively locked in a cache close to the processor, the overhead of atomic loads in \stktokens{} might be significantly less than $\tload$'s worst-case...
The processor could perhaps also (be told to) rely on the fact that race conditions should be impossible for loads from linear capabilities (which should in principle be non-aliased) and just use a non-atomic load in that case.

>>>>

Another problem is caused by the move semantics for $\tload{}$ in the presence of multiple hardware threads.
In this setting, zeroing out the source memory location must happen atomically to avoid race conditions where two hardware threads end up reading the same linear capability to their registers.
This means that a $\tload{}$ of a linear capability will need to behave like an atomic operation, similar to a compare-and-swap instruction.
This is in principle not a problem except that a compare-and-swap is significantly slower than a regular $\tload{}$ (on the order of 10x slower or more).
When using \stktokens{}, loads of linear capabilities normally happen only when a thread has stored its return data capability on the stack and loads it back from there after a return.
Because the stack is a region of memory with very high thread affinity (no other hardware thread should access it, in principle), and which is accessed quite often, we are hopeful that well-engineered caching could reduce the high overhead of atomic loads of linear capabilities.
If such memory could be (usually) kept exclusively locked in a cache close to the processor, the overhead of atomic loads in \stktokens{} might be significantly less than \texttt{load}'s worst-case...
The processor could perhaps also (be told to) rely on the fact that race conditions should be impossible for loads from linear capabilities (which should in principle be non-aliased) and just use a non-atomic load in that case.
